Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-28 paper.qmd
Page 8 numbered equation

$$\frac{1}{n}\sum_{h = 1}^{b}\sum_{i = 1}^{n_h}\sum_{j = 1}^{p} (\mathbfit{x}_{hij} - C^{(p)}_{hj})^2$$

@@

<!--To generate errors for different total number of bins-->
```{r}
## To initialize number of bins along the x-axis
bin1_vec_scurve <- 2:19 #sqrt(NROW(training_data_scurve)/2)

>>>>

$$\frac{1}{n}\sum_{h = 1}^{b}\sum_{i = 1}^{n_h}\sum_{j = 1}^{p} (\mathbfit{x}_{hij} - C^{(p)}_{hj})^2$${#eq-equation1}

@@

<!--To generate errors for different total number of bins-->
```{r}
## To initialize number of bins along the x-axis
bin1_vec_scurve <- 4:19 #sqrt(NROW(training_data_scurve)/2)
